A new tidy data structure to support exploration and modeling of temporal data

### 2019-01-24 main.Rmd
Improved English intro

<!--Suppose that temporal data consists of $N$ observational units. Given observation $i$ $(i = 1, 2, \dots, N)$, $X_{ijt}$ denotes the $j$th measurement $(j = 1, 2, \dots, p)$ indexed at a unique sequence of time points $0 \le t \le T_{i}$. 
-->
Temporal data arrives in many possible formats, as does the time context. For example, time can carry with it various time resolutions (hours, minutes, and seconds), and they are typically associated with different time zones with adjustments like summer time. It could be irregularly recorded, which is particularly true with longitudinal measurements like patient visits to a doctor's office. Temporal data also often contains rich information: multiple observational units of different time lengths, multiple and heterogeneous measured variables, multiple grouping factors. Temporal data may be occurence of events, like flight departures, that need to be induced into a regular structure.

Current time series objects, tend to be model-oriented matrices. Analysts are expected to do their own data pre-processing and take care of anything else needed to get to this stage, which leads to a myriad ad-hoc solutions and duplicated efforts.

In recent work, there has been exciting developments, that conceptually and practically streamline the pre-processing of data. Figure \ref{fig:tsibble-fit} (adapted from @r4ds) illustrates the tidy data workflow. Time series modeling and forecasting enters the picture at the *modeling* stage. While temporal data enters at the start, there isn't a current framework for getting temporal data into the matrix format for modeling. That's the part of the workflow that the work descirbed in this paper improves.

>>>>

<!--Suppose that temporal data consists of $N$ observational units. Given observation $i$ $(i = 1, 2, \dots, N)$, $X_{ijt}$ denotes the $j$th measurement $(j = 1, 2, \dots, p)$ indexed at a unique sequence of time points $0 \le t \le T_{i}$.
-->
Temporal data arrives in many possible formats, as does the time context. For example, time can carry with it various time resolutions (hours, minutes, and seconds), and they are typically associated with different time zones with adjustments such as summer time. Time can be irregularly recorded, which is often the case with longitudinal measurements such as patient visits to a doctor's office. Temporal data also often contains rich information: multiple observational units of different time lengths, multiple and heterogeneous measured variables, multiple grouping factors. Temporal data may be occurence of events, such as flight departures, that need to be induced into a regular structure.

Current time series objects tend to be model-oriented matrices. Analysts are expected to do their own data pre-processing and take care of anything else needed to allow model fitting, which leads to a myriad of ad-hoc solutions and duplicated efforts.

In recent work, there have been some exciting developments that conceptually and practically streamline the pre-processing of data. Figure \ref{fig:tsibble-fit} [adapted from @r4ds] illustrates the tidy data workflow. Time series modeling and forecasting enters the picture at the *modeling* stage. While temporal data enters at the start, there isn't a current framework for getting temporal data into the matrix format for modeling. That's the part of the workflow that the work descirbed in this paper improves.
